### 2024-09-05 draft-2/draft-2.tex
fixed typo misstating which sections are normative

This specification governs the interaction between two processes named the
{\it client} and the {\it engine}. Graphical interfaces, terminal emulators,
and scripts and utilities are examples of clients. Normative text begins at
the start of section 1 {\it Definitions} and ends after section 4 {\it Engine
Messages}.

>>>>

This specification governs the interaction between two processes named the
{\it client} and the {\it engine}. \comment{Graphical interfaces, terminal
emulators, and scripts and utilities are examples of clients.} The text of
sections 1–5 is normative (except as described in {\it Conventions} below).
